\cvsection{Experience}

\cvrole{VI Fintech}{Software Engineer}{Mar 2021 -- Present}

10-person fintech building banking infrastructure for credit unions focused on ethical, community-based lending. Serves \cvapprox{}100k+ members.

\begin{cvitems}
  \item \textbf{Retained a high-priority enterprise client} by delivering a full UI refresh of a critical form inside a legacy jQuery + custom YAML form-spec DSL; rebuilt trust through clear communication and iteration, and the client explicitly cited my work as the reason they stayed.
  \item \textbf{Improved performance of the product's highest-traffic page} by replacing slow Doctrine-based query paths (5--10s loads) with an Elasticsearch-backed approach, bringing load times to sub-1 second---work done in my first few months that's still in production today.
  \item \textbf{Solely responsible for two React Native upgrade cycles to maintain app store compliance}---first to support the new architecture, then to meet Android's 16KB page requirement---each involving 20k+ lines of changes. Both scoped and flagged well in advance, avoiding disruption for tens of thousands of members.
  \item \textbf{Modernised the mobile codebase across both upgrades:} migrated class components to hooks, adopted TanStack Query and React Hook Form, and rewrote the test suite (\cvapprox{}6k tests, solely maintained) to React Testing Library.
  \item \textbf{Built and maintained heavily-tested backend API surfaces:} contributed to a core test suite of \cvapprox{}80k tests (unit/integration/E2E with PHPUnit), with additional suites of 10k+ across other projects; introduced testing and documentation standards that made the team faster and safer when shipping changes.
  \item \textbf{Designed data and caching strategies for scale:} MariaDB schema/query optimisation with Doctrine; Redis/in-memory/HTTP caching; OpenSearch for querying and analysis over large datasets. Worked across integrator and internal-facing APIs (REST/JSON, JSON-LD/Hydra, GraphQL/OIDC, legacy XML SOAP) with robust normalisation, error handling, and versioning.
  \item \textbf{Championed accessibility and modern frontend practices:} pushed WCAG considerations into design and code review---adopted across all four user-facing products---and actively taught colleagues how and why, not just what to fix. Built interfaces with modern CSS (grid, subgrid, container queries) and semantic HTML across Bootstrap, Tailwind, and custom theming systems.
  \item \textbf{Mentored two junior developers directly;} introduced a public help-escalation channel so juniors could see seniors asking for help too---normalising the practice and making it less intimidating. Contributed to team effectiveness through code review as a teaching tool, internal documentation, and pragmatic architectural guidance (composition over inheritance, SOLID/DI, hexagonal boundaries where they paid off).
  \item Contributed GitHub Actions workflows to enforce deprecation checks and code sanitisation for the mobile app, preventing non-compliant code from reaching production.
\end{cvitems}
